Analysis and Figures for Gallego et al, 2020

### 2020-09-12 Scripts/Denoising.all.runs.Rmd
jags ready

```{r load libraries, include=FALSE}
 knitr::opts_chunk$set(warning = FALSE)

@@

outliers <- 
  all.reps %>% 
  filter(prob < 0.1 & tot < normparams.reads[1])

@@

ASV.summary %>% 
  unnest()
```

@@

```{r quick check}
# do all samples have a name
cleaned.tibble %>% 
  filter (sample == "")
# do all of them have an original sample
cleaned.tibble %>% 
  filter(original_sample == "")
# do all of them have a Hash
cleaned.tibble %>% 
  filter(is.na(Hash))
# How many samples, how many Hashes
cleaned.tibble %>% 
  summarise(n_distinct(sample), # 770
            n_distinct(Hash))   # 4571

@@

to_write_discarded <- as.tibble(all_distances[outliers]) %>% rownames_to_column("sample") %>% dplyr::select(sample, 
                                                                                                     distance_to_centroid = value)
to_write_discarded <- to_write_discarded %>% bind_rows(tibble(sample = discard.1,
                                                              distance_to_centroid = NA))
write_csv(to_write_discarded ,"../Output/discared_samples.csv")

>>>>

```{r load libraries, include=FALSE}
 knitr::opts_chunk$set(warning = FALSE, message = F)

@@

outliers <- 
  all.reps %>% 
  filter(prob < 0.075 & tot < normparams.reads[1])

@@

ASV.summary %>% 
  unnest()

@@

```{r quick check}
# do all samples have a name
cleaned.tibble %>% 
  filter (sample == "")
# do all of them have an original sample
cleaned.tibble %>% 
  filter(original_sample == "")
# do all of them have a Hash
cleaned.tibble %>% 
  filter(is.na(Hash))
# How many samples, how many Hashes
cleaned.tibble %>%
  ungroup %>% 
  summarise(n_distinct(sample), # 770
            n_distinct(Hash))   # 4571

@@

to_write_discarded <- as.data.frame(all_distances[outliers]) %>% rownames_to_column("sample") %>% dplyr::select(sample, 
                                                                                                     distance_to_centroid = 2)
to_write_discarded <- to_write_discarded %>% bind_rows(tibble(sample = discard.1,
                                                              distance_to_centroid = NA))
write_csv(to_write_discarded ,"../Output/discared_samples.csv")

### 2020-09-12 Scripts/From.asv.to.data.plankton.Rmd
jags ready

---
title: "From ASV to data.plankton"
output: html_notebook
---

This script will take the ASV table from the pipeline, and combine it with three metadata sources:
  * Taxonomical annotation
  * Biomineralization & lifestyle; these two have already been combined in the Rmarkdown "taxonomy.biom.food.env.Rmd"
  * Environmental data

@@

```{r}
library (tidyverse)
library (here)
source(here("Scripts", "eDNAindex.R"))
ASV.table  <- read_csv(here("Input", "ASV_table_all_together.csv"))
Annotation <- read_csv(here("Input", "hash.annotated.csv"))
env.data   <- read_csv(here("Input", "env.data.updated.csv"))
```

>>>>

---
title: "From ASV to data.plankton"
output:
  html_document:
    df_print: paged
---

This script will take the ASV table from the script Denoising.all.runs.Rmd, and combine it with three metadata sources:
  * Taxonomical annotation
  * Biomineralization & lifestyle; these two have already been combined in the Rmarkdown "taxonomy.biom.food.env.Rmd"
  * Environmental data

@@

```{r}
library (tidyverse)
library (here)
library (lubridate)
source(here("Scripts", "eDNAindex.R"))
ASV.table  <- read_csv(here("Input", "ASV_table_all_together.csv"))
Annotation <- read_csv(here("Input", "hash.annotated.csv"))
env.data   <- read_csv(here("Input", "env.data.updated.csv"))
```

### 2020-09-12 Scripts/Manuscript.Main.Analysis.Rmd
jags ready

This Markdown will make the part of the analysis that goes in the Manuscript: The starting point are the Abundance Table (number of reads per ASV per sample) and the key file (the ASV file has the Hash of the sequences, and the key has the actual DNA sequence). 
If you want to process the raw fastq files to obtain these two files, you have to use the pipeline available in http::/github.com/ramongallego/demultiplexer_for_dada2

>>>>

This Markdown will make the part of the analysis that goes in the Manuscript: The starting point are the Abundance Table (number of reads per ASV per sample) and the key file (the ASV file has the Hash of the sequences, and the key has the actual DNA sequence). 
If you want to process the raw fastq files to obtain these two files, you have to use the pipeline available in http::/github.com/ramongallego/demultiplexer_for_dada2.

It also generates some Supplementary Figures and data: Community composition analysis for the San Juan Islands (only Hood Canal in Figure 2 in the Manuscript) and phylum-specific plots of diversity projections and species-specific responses.
